The College Application Problem

### 2022-06-13 paper/paper.tex
korean style edits

\ifen 
We will represent approximate portfolio valuations using a fixed-point decimal with a precision of $P$, where $P$ is the number of digits to retain after the decimal point. Let $r[x] =  10^{-P}\lfloor 10^P x \rfloor$ denote the value of $x$ rounded down to its nearest fixed-point representation. Since $\bar U = \sum_{j\in \mathcal{C}} f_j t_j$ is an upper bound on the valuation of any portfolio, and since we will ensure that each fixed-point approximation is an underestimate of the portfolio's true valuation, the set $\mathcal{V}$ of  valuations observable in the fixed-point framework is finite:
\else
포트폴리오의 근사적 가치를 정확도 $P$로 구성된 고정소수점 십진수(fixed-point decimal)로 나타내자. 다, $P$는 소수점 뒤에 등장하는 숫자의 수다. 이때 $x$를 가장 가까운 고정소수점 십진수로 내림한 것을 $r[x] =  10^{-P}\lfloor 10^P x \rfloor$라고 하자. 임의의 포트폴리오의 가치가 $\bar U = \sum_{j\in \mathcal{C}} f_j t_j$를 넘을 수 없으며, 모든 포트폴리오 가치의 고정소수점 십진수 근사가 실제값보다 작게 나타내도록 한다. 따라서 고정소수점 환경에서 발생할 수 있는 포트폴리오 가치로 이루어진 집합 $\mathcal{V}$는 유한 집합이다.
\fi
\begin{equation}
\mathcal{V} = \Bigl\{0, 1\times 10^{-P}, 2\times 10^{-P}, \dots, r\bigl[\bar U- 1\times 10^{-P}\bigr], r\bigl[\bar U\bigr]\Bigr\}
\end{equation}
\ifen Then $|\mathcal{V} | = \bar U \times 10^P + 1$.
\else 그러면 $|\mathcal{V} | = \bar U \times 10^P + 1$이다.\fi

\ifen
For the remainder of this subsection, unless otherwise specified, the word \emph{valuation} refers to a portfolio’s valuation within the fixed-point framework, with the understanding that this is an approximation. We will account for the approximation error below when we prove the dynamic program’s validity. 
\else
본 항 나머지에서, 다른 언급이 없으면 포트폴리오의 ``가치''라고 하면 고정소수점 환경 안에서의 가치를 의미하며 이것이 근삿값임을 유념한다. 근사 오차는 나중에 동적 계획의 타당성을 증명할 때 처리한다.
\fi

@@

\ifen
Because $\Delta_j(v)$ is rounded down in the recursion relation defined by \eqref{recursionrelationforcostmindp} and \eqref{deltajvdef}, if $j \in \mathcal{W}[j, v]$, then the true value of $(1 - f_j) v\bigl(\mathcal{W}[j-1, v- \Delta_j(v)]\bigr) + f_j t_j$ may exceed the fixed-point valuation $v$ of $\mathcal{W}[j, v]$, but not by more than $10^{-P}$. This error accumulates additively with each school added to $\mathcal{W}$, but the number of additions is at most $m$. Therefore, where $v'(\mathcal{W})$ denotes the fixed-point valuation of $\mathcal{W}$ recorded in line \ref{vrecordedhere} of the algorithm, 
$v(\mathcal{W}) - v'(\mathcal{W}) \leq m 10^{-P}$.
\else
\eqref{recursionrelationforcostmindp}과(와) \eqref{deltajvdef}(으)로 정의된 점화식에 따라 $\Delta_j(v)$를 내림하기 때문에, $j \in \mathcal{W}[j, v]$이면 $(1 - f_j) v\bigl(\mathcal{W}[j-1, v- \Delta_j(v)]\bigr) + f_j t_j$의 실제값은 $\mathcal{W}[j, v]$의 고정소수점 가치인 $v$보다 클 수 있는데 최대한 $10^{-P}$ 만큼의 차이가 발생한다. 또한 이 오차는 $\mathcal{W}$에 학교를 추가할 때마다 가산적으로 누적되는데 추가하는 학교의 개수는 최대한 $m$이다. 따라서 알고리즘의 \ref{vrecordedhere}줄에서 기록하는 $\mathcal{W}$의 고정소수점 가치가 $v'(\mathcal{W})$일 때, $v(\mathcal{W}) - v'(\mathcal{W}) \leq m 10^{-P}$이 성립한다.
\fi

\ifen
We can define $v'(\mathcal{X})$ analogously as the fixed-point valuation of $\mathcal{X}$ when its elements are added in index order and its valuation is updated and rounded down to the nearest multiple of $10^{-P}$ at each addition in accordance with \eqref{solvemeforvwjvminusj}. By the same logic, 
$v(\mathcal{X}) - v'(\mathcal{X}) \leq m 10^{-P}$. The optimality of $\mathcal{W}$ in the fixed-point environment implies that $v'(\mathcal{W}) \geq v'(\mathcal{X})$. 
\else
$\mathcal{X}$의 원소를 지표 순서대로 추가했을 때, 각 학교를 추가하면 \eqref{solvemeforvwjvminusj}에 따라 가치를 수정하고 가장 가까운 $10^{-P}$의 배수로 내림한 값으로 $v'(\mathcal{X})$를 $v'(\mathcal{W})$와 유사하게 정의할 수 있다. 위와 같은 논리에 따라 $v(\mathcal{X}) - v'(\mathcal{X}) \leq m 10^{-P}$이다. 또한 $\mathcal{W}$가 고정소수점 환경에서 최적이므로 $v'(\mathcal{W}) \geq v'(\mathcal{X})$임을 알 수 있다.
\fi

@@

\ifen \subsection{Implementation notes} \else \subsection{알고리즘의 구현}\fi
\ifen
We chose to implement our algorithms in the Julia language (v1.8.0b1) because its system of parametric data types allows the compiler to optimize for differential cases such as when the $t_j$-values are integers or floating-point numbers. Julia also offers convenient macros for parallel computing, which enabled us to solve more and larger problems in the benchmark (Bezanson et al. 2017). We made extensive use of the DataStructures.jl package (v0.18.11, \url{github.com/JuliaCollections}). The code is available at \url{github.com/maxkapur/OptimalApplication.jl}. % Or by opening REPL and typing ]add OptimalApplication
\else
모든 알고리즘을 쥴리아 (Julia, v1.8.0b1) 언어로 구현했다. 쥴리아는 $t_j$-값이 정수 또는 부동소수점 수와 같은 특수한 경우에 대해 컴파일러가 자동으로 최적화하는 모수적 자료형(parametric data type) 기능이 있어서 유용한 선택이었다. 또한 병렬 연산을 쉽게 관리할 수 있는 매크로를 제공하므로 계산 실험의 규모를 증가할 수 있었다 (Bezanson 외 2017). DataStructures.jl 패키지(v0.18.11, \url{github.com/JuliaCollections})도 활용했다. 실험 코드는  \url{github.com/maxkapur/OptimalApplication}에서 공유한다.
\fi

\ifen
The dynamic programs, namely Algorithms \ref{ellisDP1} and \ref{ellisDP3}, were implemented using recursive functions and dictionary memoization, as described in Cormen et al. (1990, \S\,16.6). Our implementation of Algorithm \ref{ellisDP3} also differed from that described in Subsection \ref{fptashead} in that we represented portfolio valuations in \emph{binary} rather than decimal, with the definitions of $P$ and $\mathcal{V}$ modified accordingly, and instead of fixed-point numbers, we worked in integers by multiplying each element of $\mathcal{V}$ by $2^P$. These modifications yield a substantial performance improvement without changing the fundamental algorithm design or complexity analysis.
\else
동적 계획 해법인 \ref{ellisDP1}과(와) 알고리즘 \ref{ellisDP3}을(를) 재귀 함수와 사전 기록으로 구현했다 (Cormen 외 1990, \S\,16.6). 알고리즘 \ref{ellisDP3}은(는) \ref{fptashead}항에서 설명한 것과 달리, 포트폴리오의 가치를 십진수 대신 이진수로 나타냈으며 $P$와  $\mathcal{V}$의 정의를 적절히 수정했다. 그리고 고정소수점 대신 $\mathcal{V}$의 모든 원소를 $2^P$으로 곱하여 정수로 변환했다. 이런 변경은 기본 알고리즘 설계와 계산 시간 분석에 영향을 주지 않는데 성능이 많이 개선된다.
\fi

>>>>

\ifen 
We will represent approximate portfolio valuations using a fixed-point decimal with a precision of $P$, where $P$ is the number of digits to retain after the decimal point. Let $r[x] =  10^{-P}\lfloor 10^P x \rfloor$ denote the value of $x$ rounded down to its nearest fixed-point representation. Since $\bar U = \sum_{j\in \mathcal{C}} f_j t_j$ is an upper bound on the valuation of any portfolio, and since we will ensure that each fixed-point approximation is an underestimate of the portfolio's true valuation, the set $\mathcal{V}$ of  valuations observable in the fixed-point framework is finite:
\else
포트폴리오의 근사적 가치를 정확도 $P$로 구성된 고정소숫점 십진수(fixed-point decimal)로 나타내자. 다, $P$는 소숫점 뒤에 등장하는 숫자의 수다. 이때 $x$를 가장 가까운 고정소숫점 십진수로 내림한 것을 $r[x] =  10^{-P}\lfloor 10^P x \rfloor$라고 하자. 임의의 포트폴리오의 가치가 $\bar U = \sum_{j\in \mathcal{C}} f_j t_j$를 넘을 수 없으며, 모든 포트폴리오 가치의 고정소숫점 십진수 근사가 실제값보다 작게 나타내도록 한다. 따라서 고정소숫점 환경에서 발생할 수 있는 포트폴리오 가치로 이루어진 집합 $\mathcal{V}$는 유한 집합이다.
\fi
\begin{equation}
\mathcal{V} = \Bigl\{0, 1\times 10^{-P}, 2\times 10^{-P}, \dots, r\bigl[\bar U- 1\times 10^{-P}\bigr], r\bigl[\bar U\bigr]\Bigr\}
\end{equation}
\ifen Then $|\mathcal{V} | = \bar U \times 10^P + 1$.
\else 그러면 $|\mathcal{V} | = \bar U \times 10^P + 1$이다.\fi

\ifen
For the remainder of this subsection, unless otherwise specified, the word \emph{valuation} refers to a portfolio’s valuation within the fixed-point framework, with the understanding that this is an approximation. We will account for the approximation error below when we prove the dynamic program’s validity. 
\else
본 항 나머지에서, 다른 언급이 없으면 포트폴리오의 ``가치''라고 하면 고정소숫점 환경 안에서의 가치를 의미하며 이것이 근삿값임을 유념한다. 근사 오차는 나중에 동적 계획의 타당성을 증명할 때 처리한다.
\fi

@@

\ifen
Because $\Delta_j(v)$ is rounded down in the recursion relation defined by \eqref{recursionrelationforcostmindp} and \eqref{deltajvdef}, if $j \in \mathcal{W}[j, v]$, then the true value of $(1 - f_j) v\bigl(\mathcal{W}[j-1, v- \Delta_j(v)]\bigr) + f_j t_j$ may exceed the fixed-point valuation $v$ of $\mathcal{W}[j, v]$, but not by more than $10^{-P}$. This error accumulates additively with each school added to $\mathcal{W}$, but the number of additions is at most $m$. Therefore, where $v'(\mathcal{W})$ denotes the fixed-point valuation of $\mathcal{W}$ recorded in line \ref{vrecordedhere} of the algorithm, 
$v(\mathcal{W}) - v'(\mathcal{W}) \leq m 10^{-P}$.
\else
\eqref{recursionrelationforcostmindp}과(와) \eqref{deltajvdef}(으)로 정의된 점화식에 따라 $\Delta_j(v)$를 내림하기 때문에, $j \in \mathcal{W}[j, v]$이면 $(1 - f_j) v\bigl(\mathcal{W}[j-1, v- \Delta_j(v)]\bigr) + f_j t_j$의 실제값은 $\mathcal{W}[j, v]$의 고정소숫점 가치인 $v$보다 클 수 있는데 최대한 $10^{-P}$ 만큼의 차이가 발생한다. 또한 이 오차는 $\mathcal{W}$에 학교를 추가할 때마다 가산적으로 누적되는데 추가하는 학교의 개수는 최대한 $m$이다. 따라서 알고리즘의 \ref{vrecordedhere}줄에서 기록하는 $\mathcal{W}$의 고정소숫점 가치가 $v'(\mathcal{W})$일 때, $v(\mathcal{W}) - v'(\mathcal{W}) \leq m 10^{-P}$이 성립한다.
\fi

\ifen
We can define $v'(\mathcal{X})$ analogously as the fixed-point valuation of $\mathcal{X}$ when its elements are added in index order and its valuation is updated and rounded down to the nearest multiple of $10^{-P}$ at each addition in accordance with \eqref{solvemeforvwjvminusj}. By the same logic, 
$v(\mathcal{X}) - v'(\mathcal{X}) \leq m 10^{-P}$. The optimality of $\mathcal{W}$ in the fixed-point environment implies that $v'(\mathcal{W}) \geq v'(\mathcal{X})$. 
\else
$\mathcal{X}$의 원소를 지표 순서대로 추가했을 때, 각 학교를 추가하면 \eqref{solvemeforvwjvminusj}에 따라 가치를 수정하고 가장 가까운 $10^{-P}$의 배수로 내림한 값으로 $v'(\mathcal{X})$를 $v'(\mathcal{W})$와 유사하게 정의할 수 있다. 위와 같은 논리에 따라 $v(\mathcal{X}) - v'(\mathcal{X}) \leq m 10^{-P}$이다. 또한 $\mathcal{W}$가 고정소숫점 환경에서 최적이므로 $v'(\mathcal{W}) \geq v'(\mathcal{X})$임을 알 수 있다.
\fi

@@

\ifen \subsection{Implementation notes} \else \subsection{알고리즘의 구현}\fi
\ifen
We chose to implement our algorithms in the Julia language (v1.8.0b1) because its system of parametric data types allows the compiler to optimize for differential cases such as when the $t_j$-values are integers or floating-point numbers. Julia also offers convenient macros for parallel computing, which enabled us to solve more and larger problems in the benchmark (Bezanson et al. 2017). We made extensive use of the DataStructures.jl package (v0.18.11, \url{github.com/JuliaCollections}). The code is available at \url{github.com/maxkapur/OptimalApplication.jl}. % Or by opening REPL and typing ]add OptimalApplication
\else
모든 알고리즘을 쥴리아 (Julia, v1.8.0b1) 언어로 구현했다. 쥴리아는 $t_j$-값이 정수 또는 부동소숫점 수와 같은 특수한 경우에 대해 컴파일러가 자동으로 최적화하는 모수적 자료형(parametric data type) 기능이 있어서 유용한 선택이었다. 또한 병렬 연산을 쉽게 관리할 수 있는 매크로를 제공하므로 계산 실험의 규모를 증가할 수 있었다 (Bezanson 외 2017). DataStructures.jl 패키지(v0.18.11, \url{github.com/JuliaCollections})도 활용했다. 실험 코드는  \url{github.com/maxkapur/OptimalApplication}에서 공유한다.
\fi

\ifen
The dynamic programs, namely Algorithms \ref{ellisDP1} and \ref{ellisDP3}, were implemented using recursive functions and dictionary memoization, as described in Cormen et al. (1990, \S\,16.6). Our implementation of Algorithm \ref{ellisDP3} also differed from that described in Subsection \ref{fptashead} in that we represented portfolio valuations in \emph{binary} rather than decimal, with the definitions of $P$ and $\mathcal{V}$ modified accordingly, and instead of fixed-point numbers, we worked in integers by multiplying each element of $\mathcal{V}$ by $2^P$. These modifications yield a substantial performance improvement without changing the fundamental algorithm design or complexity analysis.
\else
동적 계획 해법인 \ref{ellisDP1}과(와) 알고리즘 \ref{ellisDP3}을(를) 재귀 함수와 사전 기록으로 구현했다 (Cormen 외 1990, \S\,16.6). 알고리즘 \ref{ellisDP3}은(는) \ref{fptashead}항에서 설명한 것과 달리, 포트폴리오의 가치를 십진수 대신 이진수로 나타냈으며 $P$와  $\mathcal{V}$의 정의를 적절히 수정했다. 그리고 고정소숫점 대신 $\mathcal{V}$의 모든 원소를 $2^P$으로 곱하여 정수로 변환했다. 이런 변경은 기본 알고리즘 설계와 계산 시간 분석에 영향을 주지 않는데 성능이 많이 개선된다.
\fi

### 2022-06-13 slides_08min/slides.tex
korean style edits

예산 제약 조건 하에서, 다수 확률 변수로 이뤄진 포트폴리오의 \textbf{기대 최댓값을 최대화}하는 문제이다.

@@

시장은 $m$개의 \textbf{대학교}를 포함하며, 그의 지표 집합은 $\mathcal{C} = \{ 1\dots m\}$. $j$번째 학교의 이름은 $c_j$.

@@

지원 전형료 예산, 원서를 작성하는 시간, 또는 나라의 정책에 따라 \textbf{지원 행동이 제한된다}. 본 논문은 단일 배낭 제약식 $\sum_{j\in \mathcal{X}} g_j \leq H$를 고려하며, 이때 $g_j$는 $c_j$의 \textbf{지원 비용}이라고 부른다. 
\end{frame}
} \fi

@@

The student's overall utility is the $t_j$-value associated with the \textbf{best} school she applies to and gets into:
\[\text{Utility} =\max\bigr\{t_0, \max\{t_j Z_j : j \in \mathcal{X}\}\bigr\}\]
The expected value of this quantity is called the \textbf{valuation} $v(\mathcal{X})$ of the portfolio $\mathcal{X}$. 
\end{frame}
} \else {
\begin{frame}{효용 모형}
$c_j$에 다니면 $t_j \geq 0$ 단위의 \textbf{효용}이 발생한다. Wlog, $t_j \leq t_{j+1}$.

@@

학생의 총 효용은 그가 지원하고 합격하는 \textbf{가장 좋은} 학교의 $t_j$-값:
\[\text{효용} =\max\bigr\{t_0, \max\{t_j Z_j : j \in \mathcal{X}\}\bigr\}\]
이의 기댓값은 $\mathcal{X}$의 \textbf{가치}라고 부르며 $v(\mathcal{X})$처럼 표기한다.
\end{frame}
} \fi

>>>>

예산 제약 조건 하에서, 다수 확률 변수로 이루어진 포트폴리오의 \textbf{기대 최댓값을 최대화}하는 문제이다.

@@

시장은 $m$개의 \textbf{대학교}를 포함하며, 지표 집합은 $\mathcal{C} = \{ 1\dots m\}$. $j$번째 학교의 이름은 $c_j$.

@@

지원 전형료 예산, 원서를 작성하는 시간, 또는 나라의 정책에 따라 \textbf{지원 행동에 제약이 생긴다.} 본 논문은 단일 배낭 제약식 $\sum_{j\in \mathcal{X}} g_j \leq H$를 고려하며, 이때 $g_j$는 $c_j$의 \textbf{지원 비용}이라고 부른다.
\end{frame}
} \fi

@@

The student's overall utility is the $t_j$-value associated with the \textbf{best} school she applies to and gets into:
\[\text{Utility} =\max\bigr\{t_0, \max\{t_j Z_j : j \in \mathcal{X}\}\bigr\}\]
The expected value of this quantity is called the \textbf{valuation} $v(\mathcal{X})$ of the portfolio $\mathcal{X}$. 
\end{frame}
} \else {
\begin{frame}{효용 모형}
학교 $c_j$에 다니면 $t_j \geq 0$ 단위의 \textbf{효용}이 발생한다. Wlog, $t_j \leq t_{j+1}$.

@@

학생의 총 효용은 그가 지원하고 합격하는 \textbf{가장 좋은} 학교의 $t_j$-값:
\[\text{효용} =\max\bigr\{t_0, \max\{t_j Z_j : j \in \mathcal{X}\}\bigr\}\]
이의 기댓값은 $\mathcal{X}$의 \textbf{가치}라고 부르며 $v(\mathcal{X})$로 표기한다.
\end{frame}
} \fi

### 2022-06-13 slides_15min/slides.tex
update name/url of Julia package to ~.jl
korean style edits

\ifen 
\title{The College Application Problem}
\author{Max Kapur and Sung-Pil Hong}
\institute{Seoul National University\\
Department of Industrial Engineering\\
Management Science/Optimization Lab\\
\url{maxkapur@snu.ac.kr}}
\date[\today]{June 3, 2022\\
Spring Conference of the Korean Institute of Industrial Engineers}
\else
\title[대학 입학 지원 최적화 문제]{대학 입학 지원 최적화 문제\\The College Application Problem}
\author[Max Kapur, 홍성필 교수]{Max Kapur, \underline{홍성필 교수}}
\institute{서울대학교 산업공학과\\
경영과학/최적화 연구실\\
\{maxkapur, \underline{sphong}\}@snu.ac.kr}
\date[\today]{2022년 6월 3일\\
대한산업공학회 춘계공동학술대회}
\fi

@@

\begin{itemize}
\item Investment with uncertain payoff, search for the efficient frontier recall \textbf{portfolio allocation} models. 
\item Generalizes the \textbf{knapsack problem}: Integral packing constraint, NP-completeness.
\item Objective is a \textbf{submodular set function}, but approximation results suggest college application is a relatively easy instance. 
\end{itemize}
\end{frame}
} \else {
\begin{frame}{방법론적 지향}
대학 지원 전략은 조합 최적화 중 여러 분야에 걸쳐 있다.

@@

The student's overall utility is the $t_j$-value associated with the \textbf{best} school she gets into:
\[\text{Utility} =\max\bigr\{t_0, \max\{t_j Z_j : j \in \mathcal{X}\}\bigr\}\]
When the student's application portfolio is $\mathcal{X}$, we refer to her expected utility as the portfolio's \textbf{valuation} $v(\mathcal{X})$. 
\end{frame}
} \else {
\begin{frame}{효용 모형}
$c_j$에 다니면 $t_j \geq 0$ 단위의 \textbf{효용}이 발생한다. Wlog, $t_j \leq t_{j+1}$.

@@

This case mirrors the main Korean admissions cycle, in which $h = 3, m= 202$.

@@

이것은 $h = 3, m = 202$인 한국 정시 입학 과정과 비슷한 상황이다.

>>>>

\ifen 
\title{The College Application Problem}
\author{Max Kapur}
\institute{Seoul National University\\
Department of Industrial Engineering \\
Management Science/Optimization Lab\\
\url{maxkapur@snu.ac.kr}\\}
\date{\today}
\else
\title[대학 입학 지원 최적화 문제]{대학 입학 지원 최적화 문제}
\author{Max Kapur}
\institute{서울대학교 산업공학과 \\
경영과학/최적화 연구실\\
\url{maxkapur@snu.ac.kr}\\
\vspace{0.5em}
지도 교수: 홍성필}
\date{\today}
\fi

@@

\begin{itemize}
\item Investment with uncertain payoff, search for the efficient frontier recall \textbf{portfolio allocation} models. 
\item Generalizes the \textbf{knapsack problem}: Integral packing constraint, NP-completeness.
\item Objective is a \textbf{submodular set function}, but approximation results suggest college application is a relatively easy instance. 
\end{itemize}
\end{frame}
} \else {
\begin{frame}{방법론적 지향}
대학 지원 전략은 조합 최적화의 여러 분야에 걸쳐 있다.

@@

The student's overall utility is the $t_j$-value associated with the \textbf{best} school she gets into:
\[\text{Utility} =\max\bigr\{t_0, \max\{t_j Z_j : j \in \mathcal{X}\}\bigr\}\]
When the student's application portfolio is $\mathcal{X}$, we refer to her expected utility as the portfolio's \textbf{valuation} $v(\mathcal{X})$. 
\end{frame}
} \else {
\begin{frame}{효용 모형}
학교 $c_j$에 다니면 $t_j \geq 0$ 단위의 \textbf{효용}이 발생한다. Wlog, $t_j \leq t_{j+1}$.

@@

This case mirrors the main Korean admissions cycle, in which $h = 3, m \approx 200$.

@@

이것은 $h = 3, m \approx 200$인 한국 정시 입학 과정과 비슷한 상황이다.
